Endogenous Politics and the Design of Trade Institutions\thanks{I thank Kyle Bagwell, Mostafa Beshkar, Rick Bond, Chad Bown, Nuno Limao, Giovanni Maggi, Anson Soderbery, Bob Staiger, Maurizio Zanardi, Ben Zissimos and participants in seminars at SITE for very helpful comments and discussions.}

### 2016-12-31 game-tree.tex
add dashed line in game-tree for simultaneous choice
add language to game-tree so it will switch to draft.tex to compile
fix order of moves in stage game extensive form

\begin{comment}
\documentclass[10pt]{article}

@@

\tikzset{
% Two node styles for game trees: solid and hollow
solid node/.style={circle,draw,inner sep=1.5,fill=black},
hollow node/.style={circle,draw,inner sep=1.5,fill=white}
%non node/.style={circle,draw,inner sep=.1,fill=black}
}
\begin{tikzpicture}[scale=1.5,font=\footnotesize, grow=right]
% Specify spacing for each level of the tree
\tikzstyle{level 1}=[level distance=10mm,sibling distance=8mm]
\tikzstyle{level 2}=[level distance=8mm,sibling distance=8mm]
% The Tree
\node(0)[solid node,label=above:{$G,G^*$}]{} 
child{node(1)[solid node,label=below:{$0$}]{}}
child{[white] node(2)[solid node,xshift=12,label=above:{L}]{}  
	child{[black] node(4)[solid node,label=below:{$0$}]{}}
	child{[white] node(5)[hollow node,xshift=12]{} 
	 %child[sibling distance=11mm]{[black] node(22)[solid node]{}  }
	 child{[black] node(22)[solid node,,label=below:{$-\infty$}]{}  }
	 child{[white] node(24)[solid node,xshift=12]{}
		child{[black] node(7)[solid node,label=below:{$0$}]{}}
		child{[white] node(8)[solid node,xshift=12]{}  
			child{[black] node(10)[solid node,label=below:{$0$}]{}  }
			child{[white] node(11)[solid node,xshift=14]{} }
			child{[black] node(12)[solid node,label=above:{$\infty$}]{}  }
			edge from parent node[black, xshift=20]{$\tau$} 
			}
		child{[black] node(9)[solid node,label=above:{$\infty$}]{} }
		edge from parent node[black, xshift=20]{$s$} 	
		}
	 child{[black] node(23)[solid node,label=above:{$\infty$}]{}  }
	 edge from parent node[black, xshift=20]{$e$} 	
	 }
	child{[black] node(6)[solid node,label=above:{$\infty$}]{}}
	edge from parent node[black, xshift=23]{$\bta$} 
	}
child{node(3)[solid node,label=above:{$\infty$}]{}
}
;
% information set
    \draw[solid,bend right](1)to(3);
		\draw[solid,bend right](4)to(6);
		\draw[solid,bend right](7)to(9);
		\draw[solid,bend right](10)to(12);
		\draw[solid,bend right](22)to(23);
% labels
		\node[above,xshift=3,yshift=5]at(2){$L$}; 
		\node[above,xshift=3,yshift=5]at(24){$G$}; 
		\node[above,xshift=3,yshift=5]at(5){$N$}; 
		\node[above,xshift=6,yshift=5]at(8){$G^*$}; 
		%\node[above,xshift=5,yshift=5]at(12){$L$};
		\draw[solid](5)circle(.05cm);
		\draw[solid](0)circle(.15cm);
		\node[left]at (11) {$\tau^*$};
		\node[right]at (11) {$W\left(\ga(e,s),\bm{\tau}\right),W^*\left(\ga(e^*,s^*),\bm{\tau}\right)$};
		\node[right,yshift=-10]at (11) {$\pi\left(\tau \right)-e$};
\end{tikzpicture}

>>>>

% !TEX root = ../draft.tex
\begin{comment}
\documentclass[10pt]{article}

@@

\tikzset{
% Two node styles for game trees: solid and hollow
solid node/.style={circle,draw,inner sep=1.5,fill=black},
hollow node/.style={circle,draw,inner sep=1.5,fill=white}
%non node/.style={circle,draw,inner sep=.1,fill=black}
}
\begin{tikzpicture}[scale=1.5,font=\footnotesize, grow=right]
% Specify spacing for each level of the tree
\tikzstyle{level 1}=[level distance=10mm,sibling distance=8mm]
\tikzstyle{level 2}=[level distance=8mm,sibling distance=8mm]
% The Tree
\node(0)[solid node,label=above:{$G,G^*$}]{} 
child{node(1)[solid node,label=below:{$0$}]{}}
child{[white] node(2)[solid node,xshift=12,label=above:{L}]{}  
	child{[black] node(4)[solid node,label=below:{$-\infty$}]{}}
	child{[white] node(5)[hollow node,xshift=12]{} 
	 %child[sibling distance=11mm]{[black] node(22)[solid node]{}  }
	 child{[black] node(22)[solid node,,label=below:{$0$}]{}  }
	 child{[white] node(24)[solid node,xshift=12]{}
		child{[black] node(7)[solid node,label=below:{$0$}]{}}
		child{[white] node(8)[solid node,xshift=12]{}  
			child{[black] node(10)[solid node,label=below:{$0$}]{}  }
			child{[white] node(11)[solid node,xshift=14]{} }
			child{[black] node(12)[solid node,label=above:{$\infty$}]{}  }
			edge from parent node[black, xshift=20]{$\tau$} 
			}
		child{[black] node(9)[solid node,label=above:{$\infty$}]{} }
		edge from parent node[black, xshift=20]{$e$} 	
		}
	 child{[black] node(23)[solid node,label=above:{$\infty$}]{}  }
	 edge from parent node[black, xshift=20]{$s$} 	
	 }
	child{[black] node(6)[solid node,label=above:{$\infty$}]{}}
	edge from parent node[black, xshift=23]{$\bta$} 
	}
child{node(3)[solid node,label=above:{$\infty$}]{}
}
;
% information set
    \draw[solid,bend right](1)to(3);
		\draw[solid,bend right](4)to(6);
		\draw[dashed,bend right]([xshift=2]7.center)to([xshift=2]9.center);
		\draw[solid,bend right](7)to(9);
		\draw[solid,bend right](10)to(12);
		\draw[solid,bend right](22)to(23);
% labels
		\node[above,xshift=3,yshift=5]at(2){$N$}; 
		\node[above,xshift=3,yshift=5]at(24){$G$}; 
		\node[above,xshift=3,yshift=5]at(5){$L$}; 
		\node[above,xshift=6,yshift=5]at(8){$G^*$}; 
		%\node[above,xshift=5,yshift=5]at(12){$L$};
		\draw[solid](5)circle(.05cm);
		\draw[solid](0)circle(.15cm);
		\node[left]at (11) {$\tau^*$};
		\node[right]at (11) {$W\left(\ga(e,s),\bm{\tau}\right),W^*\left(\ga(e^*,s^*),\bm{\tau}\right)$};
		\node[right,yshift=-10]at (11) {$\pi\left(\tau \right)-e$};
\end{tikzpicture}
